\begin{rSection}{Honors and Awards}
\begin{itemize}\itemsep0.45em

\item \textbf{ICML 2026 Gold Reviewer Award} \hfill 2026\\
Awarded by the International Conference on Machine Learning (ICML); top 25\% among reviewers.

\item \textbf{NRF Postdoctoral Award} \hfill 2026\\
Awarded by the National Research Foundation (Singapore); S\$250{,}000 research grant and salary over four years.

\item \textbf{Google Cloud Research Credit Award} \hfill 2026\\
Awarded by Google; US\$5{,}000 Google Cloud credits over one year.

\item \textbf{Best Research Staff Award} \hfill 2025\\
Awarded by the Institute of Data Science, National University of Singapore; 2 selected among $\sim$50 research staff.

\item \textbf{Honorable Mention for Best PhD Thesis Award} \hfill 2024\\
Awarded by the School of Computing, National University of Singapore; 5 selected among $\sim$150 PhD graduates.

\item \textbf{SIGMOD Honorable Mention for Best Artifact} \hfill 2023\\
Awarded by ACM SIGMOD; 3 selected among $\sim$600 submissions.

\item \textbf{Dean's Graduate Research Excellence Award} \hfill 2023\\
Awarded by the School of Computing, National University of Singapore; 10 awardees among $\sim$150 graduate researchers.

\item \textbf{Outstanding Undergraduate Thesis} \hfill 2019\\
Awarded by Huazhong University of Science and Technology; top 5\%.

\item \textbf{Meritorious Winner, Mathematical Contest in Modeling} \hfill 2018\\
Awarded by COMAP; top 10\% worldwide.

\item \textbf{National Scholarship} \hfill 2017\\
Awarded by the Ministry of Education of China; top 1\% at HUST.

\item \textbf{Outstanding Students} \hfill 2016\\
Awarded by Huazhong University of Science and Technology; top 1\%.

\item \textbf{Merit Student} \hfill 2016\\
Awarded by Huazhong University of Science and Technology; top 5\%.

\end{itemize}
\end{rSection}
